Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-12-14 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
rewrite cut cell grid generation description

\TODO{revise these three paragraphs to describe the slanted cell mesh}
Cut cell grids were created by starting from a uniform grid, moving all cell vertices lying underneath the orography up to the surface.  Then, the OpenFOAM utility \texttt{snappyHexMesh} was used to remove cells whose centres lay below the surface.
In addition, the utility displaces boundary vertices so that they are `snapped' to the surface \citep{openfoam2015}.  An example of the resulting cut cell grid is shown in figure~\ref{fig:grid}c.

There are two details of grid construction which mean that resulting cut cell grids can differ slightly from a typical cut cell grid as described by \citet{adcroft1997}.  First, when \texttt{snappyHexMesh} moves vertices onto the terrain surface, some points are moved horizontally.  Second, it does not create new points necessary for pentagonal cells.  An example of these effects is shown in figure~\ref{fig:snappyHexMesh} in which vertex $v$ has been moved vertically and horizontally to avoid creating a small cell.  The resultant grid, shown by thick dashed lines, contains triangular and quadrangular cells.  With a typical shaving method, cell $c$ would be pentagonal, as shown by the dotted line.  However, \texttt{snappyHexMesh} creates a quadrilateral cell.

>>>>

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.
